Structuring College Access: The Market Segment Model and College Board Geomarkets

### 2025-04-15 text/back_end_KS.qmd
rq1 dallas maps

## Dallas

@@

```{r fig-chicago-rq2-highSAT-combo, echo = FALSE, fig.align = 'center', fig.cap = "Chicago Geomarket Contribution to Purchased Student profiles by First-Generation Status, High-Range SAT orders", out.width = "100%"}
knitr::include_graphics('./../assets/images/rq2_chicago_highSAT_combo.png')
#knitr::include_graphics('./../../outputs/figures/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

>>>>

## Dallas-Fort Worth

The six Geomarkets within the Dallas-Fort Worth metropolitan area are illustrated in @fig-dallas-maps by total population across the three census periods. The Dallas-Fort Worth region represents a unique metroplex case formed by the convergence of two separate metropolitan areas, which creates a unique urban spatial structure that differs from the classic model originally proposed by @RN4982. As depicted in @fig-dallas-maps, two distinct inner-city core Geomarkets - City of Dallas and City of Fort Worth- are seperated by a centrally located suburban Geomarket encompassing Irving, Arlington, & Grand Prairie. These central Geomarkets are surrounded by the more conventional outre ring of suburban Geomarkets (Dallas Co, Collin & Rockwall Co, and West of Dallas/Ft. Worth Metroplex).

From 1980 to 2020, the population of the overall Dallas-Fort Worth metropolitan area increased substantially from approximately 2.7 Million to 6.8 Million. @fig-dallas-maps showcases all six Geomarkets experienced population growth over the three census periods. However, the most pronounced increases occured in the West of Dallas/Ft. Worth Metroplex and Collin and Rockwall Co Geomarkets, which grew from approximately 340,000 to 1.4 Million and 170,000 to 1.2 Million, respectively. These population trends, as shown in @fig-dallas-maps, suggest population growth has been partly driven by urban sprawl from the metropolitan centers - City of Forth Worth and City of Dallas - into the surrounding suburban and rural areas of the metropolitan areas. This outward expansion may also account for the comparatively larger geographic size of the West of Dallas/Fort Worth Metroplex Geomarket.

@@

```{r fig-chicago-rq2-highSAT-combo, echo = FALSE, fig.align = 'center', fig.cap = "Chicago Geomarket Contribution to Purchased Student profiles by First-Generation Status, High-Range SAT orders", out.width = "100%"}
knitr::include_graphics('./../assets/images/rq2_chicago_highSAT_combo.png')
#knitr::include_graphics('./../../outputs/figures/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png
```

```{r fig-dallas-maps, echo = FALSE, fig.align = 'center', fig.cap = "Dallas-Forth Worth Geomarkets, Total Population 1980-2020", out.width = "100%"}
knitr::include_graphics('./../assets/images/dallas_maps.png')
#knitr::include_graphics('./../../outputs/figures/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```
